### 2016-09-07 notions.tex
beginning to address JK's comments in notions.tex

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
anything at all?}

@@

\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
and in the general case I think the former is what we want.} \jnote{I also changed
the definition so the adversary has to find $r$ {\bf unique} inputs on which
there is an error.}

\begin{figure}[htp]
\centering
\fpage{.65}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{Q} \gets \emptyset$ \\
$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if ($a \neq q(S)$ and $q \not \in \mathcal{Q}$) then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
Return~$(a,q(S))$
}
}
\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

@@

\subsection{Privacy}
\jnote{Define appropriate notion of min-entropy for our setting.
Define one-wayness.}

>>>>

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \tsnote{Email discussion.} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
yes, if for no other reason than to allow~$A$ to know when it asking
a pointless query.  But also it will make no difference to the
provable correctness of the constructions we consider.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.}
\tsnote{I don't see how this correctness notion is specialized to
  set-multiplicity data structures.  I don't think we actually
  specialize notions in any way until, maybe, the OW privacy notion.
  It is true that we only deliver concrete results for set-multiplicty
data structures, however.}\jnote{Why does $A$ output
anything at all?}\tsnote{To signify it is finished execution.  Matter
of taste, I'm not hardover about it.}

@@

\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
and in the general case I think the former is what we
want.}\tsnote{This may have implications for the efficiency of
reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
counter and returned this was to avoid~$A$ be forced to evalutate
queries of unknown computational cost.} 
%\jnote{I also changedthe definition so the adversary has to find $r$
% {\bf unique} inputs on which there is an error.}

\begin{figure}[htp]
\centering
\fpage{.65}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{C} \gets \emptyset$; $\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
if $q \in \mathcal{C}$ then Return $\bot$\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
$\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
Return~$(a,q(S))$
}
}
\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

@@

\newcommand{\leak}{{\sf leak}}
\subsection{Privacy}
\jnote{Define appropriate notion of min-entropy for our setting.
Define one-wayness.}
